---
title: Do reaction times differ between women and men?
#date: "`r Sys.Date()`"
authors:
  - name: Owen L. Petchey
    email: owen.petchey@ieu.uzh.ch
    address: University of Zurich
    corresponding_author: yes
  - name: Your Name
    email: your@name.com
    address: Your University
abstract: |
  This is the abstract.

  It consists of two paragraphs.
acknowledgements: |
  This is an acknowledgement.

  It consists of two paragraphs.
keywords:
  - key
  - dictionary
  - word
#fontsize: 12pt
#spacing: halfline # could also be oneline
#classoptions:
#  - endnotes
bibliography: mybibfile.bib
output: rticles::oup_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
knitr::opts_chunk$set(message = FALSE) # By default, hide messages
knitr::opts_chunk$set(fig.pos = 'p') # Places figures on their own pages
knitr::opts_chunk$set(out.width = '100%', dpi=300) # Figure resolution and size
knitr::opts_chunk$set(fig.env="figure") # Latex figure environment

library(xtable) # Creates tables that follow OUP guidelines; other options, such as kable, may also be workable
library(readr)
library(dplyr)
library(ggplot2)
library(skimr)
library(schoRsch)
```

# Introduction

Look at doi 10.4103/2229-516X.157168

(Here are two sample references: @Feynman1963118 [@Dirac1953888]. Bibliography will appear at the end of the document.)

(We can cross-reference sections and subsections as follows: Section \ref{materials-and-methods}.)


# Materials and methods


# Results

```{r}
class_RTs <- read_csv("data/My reaction time (2020) - Form responses 1.csv")
names(class_RTs) <- c("Timestamp", "ID", "Gender", "Pref_Reaction_time_1",
                      "Verbal_memory_score", "Number_memory_score",
                      "Visual_memory_score",
                      "Weight_kgs", "Handed", "Nonpref_Reaction_time_ave",
                      "Pref_Reaction_time_2", "Pref_Reaction_time_3", 
                      "Pref_Reaction_time_4", "Pref_Reaction_time_5",
                      "Pref_Reaction_time", "Random_number")
```

Numbers of sampled women and men, and the mean and median reaction time, and the standard error of the mean (SEM) (Table \ref{tab:summary-stats}.)

```{r summary-stats, results="asis"}
summary_stats <- class_RTs %>%
  group_by(Gender) %>%
  summarise(number = n(),
            mean = mean(Pref_Reaction_time),
            median = median(Pref_Reaction_time),
            SEM = sd(Pref_Reaction_time)/sqrt(n()))
tab <- xtable(summary_stats, caption="This is the table caption", label="tab:summary-stats")
print(tab, type = "latex", comment = FALSE)
```

You can reference this figure as follows: Fig. \ref{fig:prt-histograms}.

```{r prt-histograms, fig.cap="This is the first figure.", fig.height=3, fig.width=3, out.width="50%", fig.align="center"}
## Now make a figure containing two histograms histograms (i.e. two "facets"), one for each gender
ggplot(data=class_RTs, aes(x=Pref_Reaction_time)) +
  geom_histogram() +
  facet_grid(~ Gender)
```



```{r}
## Perhaps filter out some extreme values
lower_limit <- 50
upper_limit <- 500
class_RTs_filtered <- class_RTs %>%
  filter(Pref_Reaction_time > lower_limit,
         Pref_Reaction_time < upper_limit)
```

We filtered the reaction time data to remove those less than `r lower_limit` and greater than `r upper_limit` milliseconds.

You can reference this figure as follows: Fig. \ref{fig:prt-boxplot}.


```{r prt-boxplot, fig.cap="This is the second figure, using filtered data.", fig.height=3, fig.width=3, out.width="50%", fig.align="center"}
class_RTs_filtered %>%
  ggplot(aes(x=Gender, y=Pref_Reaction_time)) +
  geom_boxplot() +
  geom_jitter(width=0.05)
```

```{r t-test-filtered}
my_ttest <- t.test(Pref_Reaction_time ~ Gender,
                   data = class_RTs_filtered,
                   var.equal=TRUE)
```

T-test on the filtered data: t = `r round(my_ttest$statistic)`.

# Discussion






***Note:*** the last section in the document will be used as the section title for the bibliography.

# References
